A Short and Mechanized Consistency Proof for Dependent Type Theory

### 2023-12-31 paper/paper.tex
Add the alt intro inv rules for pi

>>>>

Lemma~\ref{lemma:logreldeter} enables us to derive the following
alternative introduction and inversion principles for \rref{I-Pi}.
\begin{lemma}[Pi Intro Alt]
  \label{lemma:piintroalt}
  Suppose the following two statements hold:
  \begin{itemize}
  \item $[[Interp I i A S]]$
  \item $[[forall a, a in S implies (# exists S0 , Interp I i B {a} S0 #)]]$
  \end{itemize}
  Then we have $[[Interp I i Pi A B { b | forall a, (# a in S , forall
    S0, (# Interp I i B {a} S0,  b a in F a #) #) }]]$
\end{lemma}
\begin{proof}
  Let $[[F]]$ be the relation defined as follows:
  \[ (a,S) \in [[F]] \iff [[Interp I i B {a} S]] \]
  By the second bullet from the premise and
  Lemma~\ref{lemma:logreldeter}, $[[F]]$ is a function that is total
  on the set $[[S]]$. The conclusion then trivially follows from
  \rref{I-Pi}.
\end{proof}

\begin{lemma}[Pi Inv Alt]
  \label{lemma:piinvalt}
  Suppose $[[Interp I i Pi A B S]]$, then there exists some $[[S0]]$
  such that the following constraints hold:
  \begin{itemize}
  \item $[[Interp I i A S0]]$
  \item $[[forall a, (# a in S0 implies (# exists S1 , Interp I i B {a}
    S1 #) #)]]$
  \item $[[S = { b | forall a, (# a in S0 , forall
    S1, (# Interp I i B {a} S1,  b a in F a #) #) }]]$
  \end{itemize}
\end{lemma}
\begin{proof}
  Immedaite from Lemmas~\ref{lemma:interpinv} and \ref{lemma:logreldeter}.
\end{proof}

% The combination of Lemmas~\ref{lemma:piintroalt} and
% \ref{lemma:piinvalt} reveals what we truly want to capture with
% \rref{I-Pi}. A function type is semantically well-defined if its input
% type is well-defined, and its output type is defined for each valid
% inahbitant of its input type.
